---
title: "Data Visualization"
date: `r Sys.Date()`
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

## Task 1

- Load the tidyverse package here:

```{r}

```


## Task 2

- Run this code to observe the data set

```{r}
movies <-  read_csv("https://bit.ly/35qiemi")

movies
```

## Task 3

- Insert `movies` data set in ggplot:

```{r}

ggplot(data =     )

```

## Task 4

- Map domestic_gross to x-axis, worldwide_gross to y-axis

- Set the color of point to blue

- Set the shape of point to any one point (1 or 2... or 24)

- Set the size of points to 5

```{r}

ggplot(data = movies) +
  geom_point(
    mapping = aes(x = , y = ),
    color = "",
    shape = ,
    size =
    )
```

## Task 5

- Set the color aesthetics to `genre` and see what happens:


```{r}

ggplot(data = movies) +
  geom_point(mapping = aes(
    x = domestic_gross,
    y = worldwide_gross,
    color =
    ))
             
              
```

## Task 6

- Apply the aesthetics globally such that:
 `production_budget` is mapped to x-axis and
 `domestic_gross` is mapped to y-axis for all the plots.

- Also, correct the positions of "+" sign

- Hint: ggplot(data= ____, mapping = aes(x= __, y= __))

```{r}

ggplot(data = movies, )
+geom_point()
+geom_smooth()



```

## Task 7

- Change the color of points in geom_point to 'orange'

- Change the linetype in geom_smooth to 'dashed'.

- Hint: 
   `linetype= "type_of_line"` changes the linetype and 
   `color= "desired_color"` changes the color.

```{r}
ggplot(
  data = movies,
  mapping = aes(
    x = production_budget,
    y = domestic_gross
  )
) +
  geom_point() +
  geom_smooth()

```

## Task 8

- Create a bar plot to visualize the counts of `genre` and also, 
  fill the bar plot according to mpaa_rating:

```{r}

ggplot(data = ) +
  geom_bar(aes(x = , fill = ))

```

#Task 9:

- Task 8 creates a bar_chart with default: position='stack'.

- Copy the ggplot code from task8 and modify the position 
  to 'dodge' to create a dodged bar graph.

- Hint: the dodge position should be mentioned outside aes()

- Finally, save the plot into `myplot` 

```{r}

myplot

```

## Task 10

- Label the graph from task9 with with labs()

- Set the title: "Movie genre with mpaa rating"

- Set the subtitle: "Year 1946-2016"

- Set the caption: "Source: Tidytuesday"

- Set the tag: "Fig 1"

- Label x-axis (x) as: "Different movie genre"

- Label y-axis (y) as: "Total number of movies released"

- Label the legend as: "Movie ratings"

```{r}









```

## Task 11

- Create a box plot for `worldwide_gross`.

```{r}

ggplot(data = movies) +
  geom_boxplot(
    mapping =
      aes(y = worldwide_gross)
  )

```

#Task 12

- Create a box plot of `worldwide_gross` for each genre.

```{r}

ggplot(data = ) +
  geom_boxplot(
    mapping =
      aes(x = , 
          y = worldwide_gross)
  )

```

## Task 13

- Here, gross is the scatter plot between 
  `production budget` and `domestic gross`.
  
- Create a subplot with 2 columns based on genre

```{r}
gross <- ggplot(
  data = movies,
  aes(
    x = production_budget,
    y = domestic_gross
  )
) +
  geom_point()


gross + 
  facet_wrap(facets = ~  , ncol =   )

```

## Task 14

- Here, gross is the scatter plot between production budget and domestic gross.

- create a subplot based on genre and mpaa_rating.

```{r}

gross +
  facet_grid(genre~        )


```
